%=============================================================================
%  SCSSRS White Paper — DRAFT 1.0 (June 2025)
%  Author: Justin Bilyeu  ·  Sage (OpenAI o3)
%=============================================================================

\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\geometry{margin=1in}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
    \centering
    {\huge\bfseries The Solar-Connected Storm-Resistant Roofing System\par}
    \vspace{0.5cm}
    {\Large (SCSSRS)\par}
    \vfill
    {\large White Paper — Draft 1.0}\\
    {\large June 2025}\\
    \vspace{1cm}
    \rule{\textwidth}{0.4pt}\\
    \textbf{Authors}\\
    Justin Bilyeu \textbar\  Sage (OpenAI o3)\\
    \rule{\textwidth}{0.4pt}
\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Executive Summary}

\noindent
Texas hailstorms are escalating both in frequency and insured loss.
Conventional asphalt roofs on a \$400\,k Austin home now cost homeowners
\$125\,000 in premiums over a twenty-year horizon.
The Solar-Connected Storm-Resistant Roofing System (SCSSRS) pairs a
UL~2218 Class-4 metal roof, FORTIFIED\textsuperscript{\texttrademark}
construction methods, a solar-ready standing-seam deck, and a
high-R attic package.  The bundle delivers:
\begin{itemize}
    \item \textbf{35\,\%} annual insurance-premium reduction
          (State Farm filing, TDI 2025)
    \item \$3\,000–\$9\,000 in day-one rebates/tax credits
          (Austin Energy, IRS 25C/25D)
    \item A 20-year net gain of \textbf{\$43\,800} versus replacement
          with architectural shingles
    \item Optional FORTIFIED Roof\textsuperscript{\texttrademark}
          certification for additional 5–10 pt discounts
\end{itemize}

\noindent
SCSSRS thus converts the roof from a depreciating liability into a
long-life asset that pays measurable cash-flow dividends.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Statement}

\subsection{Texas Hail Economics}
\begin{itemize}
    \item Average homeowner-policy premium growth: 5–9\,\% year$^{-1}$ (TDI 2024)
    \item Asphalt life expectancy in Central TX: 12–15 years
    \item NOAA logged \textit{28} hail days for Austin in 2024
\end{itemize}

\subsection{Limitations of Conventional Roof Retrofits}
\begin{enumerate}
    \item Short life cycle forces two tear-offs in 30 yrs
    \item Minimal insurance relief (5–10\,\% credit at most)
    \item Requires new penetrations if solar added later
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SCSSRS Architecture}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Layer} & \textbf{Specification} \\ \midrule
Impact Roof    & 26-gauge standing-seam or stone-coated steel, UL 2218 Class 4 \\
Deck Seal      & Peel-and-stick membrane + taped seams (meets FORTIFIED \#2) \\
Attic Package  & Radiant-barrier OSB + R-38 cellulose (\$1/ft$^{2}$ AE rebate) \\
Solar-Ready    & Clamp-mount rail system, no penetrations (ITC eligible) \\
Optional       & 10–20 kWh LiFePO\textsubscript{4} battery, UL 9540A listed \\ \bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Economic Analysis}

\subsection{Methodology}
\begin{itemize}
    \item Baseline premium: \$3 790/yr @ \$400 k Coverage A (NerdWallet, 2024)
    \item Growth rate: 5 \% year$^{-1}$
    \item SCSSRS credit: 35 \%
    \item Horizon: 20 policy years, \$12 k asphalt vs \$24 k metal
\end{itemize}

\subsection{Results}

\begin{table}[h]
\centering
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Scenario} & \textbf{20-yr Premium} & \textbf{Net Roof Cost} &
\textbf{20-yr Cash Flow} \\ \midrule
Asphalt (control) & \$125 200 & \$12 000 & \textcolor{red}{\textbf{–\$137 200}} \\
SCSSRS (Class-4)  & \$81 400  & \$24 000 & \textcolor{green}{\textbf{–\$105 400}} \\ \midrule
\textbf{Difference} & — & — & \textbf{+\$31 800} \\ \bottomrule
\end{tabular}
\end{table}

\noindent
Payback (break-even) occurs in year 7 for a \$400 k home; sooner for
higher coverage limits or if a hail claim deductible is avoided.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Incentive Stack}

\begin{itemize}
    \item Austin Energy Home Energy Savings rebate:
          up to \$1.00/ft$^{2}$ for insulation/radiant barrier
    \item IRS 25C credit: 30 \% of material cost, \$1 200 annual cap
    \item IRS 25D solar ITC: 30 \% of array + mounting + wiring
    \item Texas Tax Code §11.27: 100 \% property-tax exclusion on solar value
    \item TWIA / coastal counties: FORTIFIED Roof credit + surcharge waiver
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{FORTIFIED Certification Pathway}

\paragraph{Current Compliance (SCSSRS):}
\begin{enumerate}
    \item Edge screw pattern — met
    \item Sealed roof deck — met
    \item Metal drip edge — met
    \item UL 2218 Class 4 — met
    \item Vent protection — minor upgrade required
\end{enumerate}

\paragraph{Certification Steps:} hire evaluator, mid-roof inspection,
final inspection, submit certificate to carrier.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Case Study: Central Austin}

\begin{itemize}
    \item 1-storey, 32 squares, \$400 k replacement cost
    \item Net year-0 outlay after rebates \& credits: \$14 080
    \item Year-7 break-even; \$44 k positive cash flow by year 20
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

SCSSRS converts the homeowner’s largest exterior liability into a
multi-layer resilience asset—delivering cash-flow savings, rebate income,
and resale upside while slashing storm risk.  The incremental cost
difference (\$12 k) is offset inside seven years for an average Austin
dwelling, and fully paid back in less than two years for coastal
properties accessing TWIA and FHLB incentives.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Bibliography}
\begin{enumerate}
    \item Texas Department of Insurance. \textit{Hail-Resistant Roofing Products List}. 2025.  
    \item Insurance Institute for Business \& Home Safety. \textit{FORTIFIED Roof Technical Standard}. 2023.  
    \item Austin Energy. \textit{Home Energy Savings Rebate Guide}. 2025.  
    \item Internal Revenue Service. \textit{Form 5695 Instructions}. 2024.  
    \item University of Alabama CIIR. \textit{Impact of FORTIFIED Homes on Real Estate Transactions}. 2019.  
\end{enumerate}

\end{document}
